Illusory Finger Stretching and Somatosensory Responses

### 2025-03-19 manuscript.qmd
Trying to sort out conversion to data frame

#make eegdata dataframes
eegdata <- data.frame(eegdata)
eegdata_exp <- data.frame(eegdata_exp)
colnames(eegdata) <- c('V1','V2','V3','V4')
colnames(eegdata_exp) <- c('V1','V2','V3','V4')

>>>>

#make eegdata dataframes
eegdata <- data.frame(as.matrix(eegdata))
eegdata_exp <- data.frame(as.matrix(eegdata_exp))
colnames(eegdata) <- c('V1','V2','V3','V4')
colnames(eegdata_exp) <- c('V1','V2','V3','V4')
